Blowship - Anonymous Communication via a Central Server

### 2014-03-10 paper.tex
Falling balls

@@

>>>>

\subsection{Peer Discovery & MITM brainstorming}

Lying about who's online - If you want to send a message to a real node ``B'' but B is not listed as online, you won't send a message. However, if he lists ``B'' as online, ``B'' can be used to route messages validly by everyone.

Chain verification - Keep a web of trust with the length of the path to a person inversely proportional to how trusted they are. Share web of trust with those we communicate with - only share nodes with a certain level of trust, and then trust nodes discovered this way with diminished trust.

If initial trust is only spread through person to person contact, then assigning negative trust is valuable because it reduces the value of colluding human nodes.

* Have nodes sign messages as they pass through, so that the path can be tested/verified.

@@

Users should maintain a list of known keys to make stuff good.
